---
title: "CLinical Data Management Wksp 2026"
author: "AFMC, Pune"
format: html
execute:
  echo: false
bibliography: references.bib
---

# Introduction

This demo is to represent the workflow as given by a seminal paper.[@ong2019]

## Packages

Packages neeed to be installed once and called using a function `library()` everytime before use in a session.

```{r}
# install packages
# install.packages("here")
# install.packages("rio")
# install.packages("tidyverse")
# install.packages("gtsummary")
# Load packages
library(here)
library(rio)
library(tidyverse)
library(gtsummary)

```

# Load Data

```{r}
# Path
path <- here("data",
     "simulated_clinical_04july2026.xlsx")
# Import
df1 <- import(path, setclass = "tibble")

# Path
path <- here("data",
     "site04_04july2026.xlsx")
# Import
df2 <- import(path, setclass = "tibble")

df <- rbind(df1, df2)
```

# Understand and clean/wrangle Data

```{r}
# ## Dimensions
df |> 
  dim()

# Glipmpse
df |> 
  skimr::skim()

```

# Make some plots/ figures

```{r}
df |> # dataset specification
  ggplot() + # call for a plot
  geom_bar( # mention geometry
    aes(x = Sex) # mention aesthestics incl x and y axis
  ) +
  labs(title = "My first plot") # additional settings
```

```{r}
df |> 
  ggplot() +
  geom_point(
    aes(x = Age, y = BMI)
  ) +
  geom_smooth(aes(x = Age, y = BMI), method = lm) +
  labs(title = "My first plot",
       subtitle = "My first plot subtitle")
```

# Make some tables

## Participant characteristics

```{r}
df |> 
  select(Age, Sex, BMI, Alcohol,HbA1c, Study_Arm) |> 
  tbl_summary(by = Study_Arm) |> 
  add_p()
```

# Discussion

Thisn my discussion with a reference

# References
